\textbf{Implementation of autonomous line following robot using FPGA and camera module}

### 2021-02-07 CA_Article/article.tex
Update article.tex
Update the value of double integral
Update article.tex
change log value
change 4 to 2

		\begin{equation}
			\left\{
				\begin{aligned}
					x_{\text{new}} &= | \text{width\_of\_image} / 4 - x_0 | \\
					y_{\text{new}} &= -y_0\\
				\end{aligned}
			\right.
		\label{eq:sysChange}
		\end{equation}

@@

		\begin{equation}
			1 - \left ( \frac{x}{405}\right) + 
			\frac{\left ( \frac{x}{405}\right) ^2}{2}  -
			\frac{\left ( \frac{x}{405}\right)^3}{6}
		\end{equation}

		\begin{flushright}
			\footnotesize Coefficient “405” is used for values normalization \\
			$e$( 0.3, 1 ) to x( -1.066, 0 ), 430 = 405*1.066
		\end{flushright}
		\vspace{1cm}

@@

		\begin{equation}
		\begin{aligned}
			\int_0^{430} \int_0^{320} 
			\left ( 1 + \frac{y}{430}\right )
			\left (  
			1 - \left ( \frac{x}{405}\right) + 
			\frac{\left ( \frac{x}{405}\right) ^2}{2}  -
			\frac{\left ( \frac{x}{405}\right)^3}{6}
			\right )
			&x
			dx
			dy\\
			&\approx 1,88071 \times 10^7 
		\end{aligned}
		\end{equation}

@@

		\begin{equation}
			\log_{2}1887100 \approx 24,16 \Rightarrow 25
		\end{equation}

@@

		\begin{enumerate}
			\item 
			Shift to the right by 16 bits: (0;18807100) $\Rightarrow$ (0;286)

@@

\section*{Implementation}
\noindent In our project we employ following devices and software tools:
\begin{enumerate}
	\item 
	Cyclone \RomanNumeralCaps{4} FPGA board based on Altera EP4CE6E22C8N chip of low-cost and low-power Cyclone \RomanNumeralCaps{4} FPGA device family. The board appearance shown on figure \ref{fig:im1}

@@

One of the main algorithm parameter is the threshold of binarization. It depends on the color of line, lightning and sensitivity of the camera. We going to implement additional algorithm in order to automatize threshold determining. An algorithm may use first few frames for computing stable threshold value.

>>>>

		\begin{equation}
			\left\{
				\begin{aligned}
					x_{\text{new}} &= | \text{width\_of\_image} / 2 - x_0 | \\
					y_{\text{new}} &= -y_0\\
				\end{aligned}
			\right.
		\label{eq:sysChange}
		\end{equation}

@@

		\begin{equation}
			m(x) = 1 - \left ( \frac{x}{405}\right) + 
			\frac{\left ( \frac{x}{405}\right) ^2}{2}  -
			\frac{\left ( \frac{x}{405}\right)^3}{6}
		\end{equation}

		\begin{flushright}
			\footnotesize Coefficient “405” is used for values normalization \\
			$e$( 0.3, 1 ) to x( -1.066, 0 ), 430 = 405*1.066

		\end{flushright}
		\vspace{1cm}

@@

		\begin{equation}
		\begin{aligned}
			\int_0^{430} \int_0^{320} 
			\left ( 1 + \frac{y}{430}\right )
			\left (  
			1 - \left ( \frac{x}{405}\right) + 
			\frac{\left ( \frac{x}{405}\right) ^2}{2}  -
			\frac{\left ( \frac{x}{405}\right)^3}{6}
			\right )
			&x
			dx
			dy\\
			&\approx 1,96968 \times 10^7 
		\end{aligned}
		\end{equation}

@@

		\begin{equation}
			\log_{2}19696800 \approx 24,23 \Rightarrow 25
		\end{equation}

@@

		\begin{enumerate}
			\item 
			Shift to the right by 16 bits: (0;19696800) $\Rightarrow$ (0;300)

@@

\section*{Implementation}
\noindent In our project we employ following devices and software tools:
\begin{enumerate}

	\item 
	Cyclone \RomanNumeralCaps{4} FPGA board based on Altera EP4CE6E22C8N chip of low-cost and low-power Cyclone \RomanNumeralCaps{4} FPGA device family. The board appearance shown on figure \ref{fig:im1}

@@

One of the main algorithm parameter is the binarization threshold. It depends on the color of line, lightning and sensitivity of the camera. We going to implement additional algorithm in order to automatize threshold determining. An algorithm may use first few frames for computing stable threshold value.
